---
title: "Assignment 1"
author: "Vivekanand Kulkarni 19200231"
date: "09/10/2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task 1 Manipulation
Question 1
Load the dataset EurostatCrime2017.csv. Notice that the first column of the csv
contains the names of the countries that must be read as row names
```{r Load the dataset EurostatCrime2017.csv, echo=TRUE}
Eurocrimedata=read.csv("C:\\Users\\Vivek\\Downloads\\EurostatCrime2017.csv", header = TRUE, row.names = 1)
Eurocrimedata
```

## Question 2
The size (number of rows and columns) and the structure of this dataset.
```{r, echo=TRUE}
str(Eurocrimedata)
nrow(Eurocrimedata)
ncol(Eurocrimedata)
```

## Question 3
Please consider NA values as 0 in this case.
Add a new column called All Theft
Remove the columns: Theft, Theft of a motorized land vehicle, Burglary, and
Burglary of private residential premises.
```{r, echo=TRUE}
Eurocrimedata$Theft[is.na(Eurocrimedata$Theft)] <-0
Eurocrimedata$Burglary[is.na(Eurocrimedata$Burglary)]<- 0
Eurocrimedata$Burglary_of_private_residential_premises[(is.na(Eurocrimedata$Burglary_of_private_residential_premises))]<-0
Eurocrimedata$Theft_of_a_motorized_land_vehicle[is.na(Eurocrimedata$Theft_of_a_motorized_land_vehicle)]<-0
```

```{r, echo=TRUE}
Eurocrimedata$All_Theft<-(Eurocrimedata$Theft+Eurocrimedata$Theft_of_a_motorized_land_vehicle+Eurocrimedata$Burglary+Eurocrimedata$Burglary_of_private_residential_premises)
Eurocrimedata$All_Theft
str(Eurocrimedata)
```

```{r, echo=TRUE}
NewEurocrimedata<-data.frame(Eurocrimedata)
NewEurocrimedata <-subset(Eurocrimedata, select = -c(7,8,9,10))
NewEurocrimedata
```
## Question 5 and 6
Remove the countries with missing data from the data frame.
Adding new data frame containing complete cases.
```{r,echo=TRUE}
newdf<-NewEurocrimedata[!complete.cases(NewEurocrimedata),]
Countries<-row.names(newdf)
Countries
a<-NewEurocrimedata[complete.cases(NewEurocrimedata),]
str(a)
```
## Task 2: Analysis
The 3 most common crimes in Ireland in 2017 and the country which the highest overall record of offences
```{r, echo=TRUE}
Top<- sort(a['Ireland',],decreasing = TRUE)
Top[1]
Top[2]
Top[3]
```
```{r, echo=TRUE}
Highestoffense<-sort(apply(a,MARGIN=1,FUN= sum),decreasing = TRUE)
Highestoffense[1]
```
## Task3 Creativity.
All the crimes individually are plotted in form of barplot,boxplot and pair.
In case of bar plot x- axis are the countries.
In case of boxplot we can see that most of the graphs are negatively skewed.

```{r, echo=TRUE}
barplot(NewEurocrimedata$Sexual.violence)
barplot(NewEurocrimedata$Intentional_homicide)
barplot(NewEurocrimedata$Attempted_intentional_homicide)
barplot(NewEurocrimedata$Assault)
barplot(NewEurocrimedata$Kidnapping)
barplot(NewEurocrimedata$Robbery)
barplot(NewEurocrimedata$Unlawful_acts_involving_controlled_drugs_or_precursors)
barplot(NewEurocrimedata$All_Theft)
boxplot(NewEurocrimedata$Intentional_homicide)
boxplot(NewEurocrimedata$Attempted_intentional_homicide)
boxplot(NewEurocrimedata$Assault)
boxplot(NewEurocrimedata$Kidnapping)
boxplot(NewEurocrimedata$Robbery)
boxplot(NewEurocrimedata$Unlawful_acts_involving_controlled_drugs_or_precursors)
boxplot(NewEurocrimedata$All_Theft)
pairs(NewEurocrimedata)
```